\cvsection{Work Experience}

	\cvexperience{AI Engineer}{Technology Reply}
	{Italy}{02/2024 – present}
	\begin{itemize}
		\item R\&D of Machine Learning and GenAI techniques to improve the software development cycle and IT infrastructure operations.
		\item My day-to-day activities include the identification of critical business use cases in which GenAI or ML-based solutions can be leveraged to solve them.
	\end{itemize}
		
	\medskip

    \cvexperience{Machine Learning Research Engineer}{UNIMOL}
	{Italy}{04/2023 – 10/2023}
	\begin{itemize}
            \item Served as machine learning scientist in the Nova Tellus project (funded by the EU), a novel system supporting agricultural practices via big data analytics and machine learning.
            \item Development and validation of a set of ML algorithms, working with sensor data, to support precision agriculture practices.
	\end{itemize}
	
	\medskip

    \cvexperience{Software Engineer}{Freelancer}
	{Italy}{11/2020 – 01/2021}
	\begin{itemize}
            \item Design and development of a life-saving mobile app to call nearby BSLD operators in case of heart-related emergencies.
            \item Implemented the mobile app, admin panel, and real-time notifications for immediate response during the emergencies.
	\end{itemize}
        	
	\medskip
	
    \cvexperience{Machine Learning Research Engineer}{UNIMOL}
	{Italy}{04/2019 – 10/2020}
	\begin{itemize}
		\item Served as machine learning scientist in the ATTICUS project (funded by the EU), an IoMT system for the monitoring and early detection of health anomalies.
		\item Development and validation of several machine-learning approaches to detect health-related anomalies, a mobile app, and the CI/CD of all the system components (\emph{i.e.,} backend, frontend, database, DSS, and ML services).
	\end{itemize}

	\medskip

    \cvexperience{Software Engineer}
	{Freelancer}{Italy}{03/2020 – 04/2020}
	\begin{itemize}
            \item Design and development of a chatbot, fine-tuned on scientific articles to answer questions on COVID-19, to serve as a reliable source of information to mitigate the diffusion of fake news.
            \item Implemented a Q\&A pipeline using BERT and Flask.
	\end{itemize}

	\medskip

    \cvexperience{Software Engineer}{Freelancer}
	{Italy}{02/2019 – 04/2019}
	\begin{itemize}
            \item Design and development of a search engine specifically designed to easily retrieve court decisions.
            \item The system includes a simple ETL pipeline for the ingestion of the documents served via Elasticsearch.
	\end{itemize}